\documentclass[9pt,a4paper]{article}
\usepackage[english]{babel}
\input{myMacros.tex}
\geometry{a4paper, reset, left=3cm,right=2.5cm}

% \graphicspath{{../images}}
% 
\author{ }
% \bibliographystyle{ieeetr}
% adjust the page margins

\begin{document}
\title {Details Regarding Acquisition of Research Funds}
\date{}
\maketitle

\subsection*{Summary of Funding Acquisition}

Over the course of my career, I have successfully participated in and contributed to numerous national and international research funding initiatives. These include mobility funds (independently acquired external funds), as well as grants from organizations such as the National Natural Science Foundation of China (NSFC). My involvement has encompassed performing preliminary exploratory research, engaging with and convincing industrial partners to join user groups (a mandatory requirement for Belgium’s Flanders Make SBO initiatives), and drafting successful proposals. Below are specific details of key research funds acquired.

\subsection*{Mobility Funds}

\begin{itemize}
    \item \textbf{Outstanding Young Scientific Research Talents International Cultivation Project Fund, Guangdong Province Department of Education (2019):}  
    Awarded for outstanding scientific contributions, this scholarship enabled me to visit KU Leuven as an International Scholar, facilitating valuable cross-institutional collaboration and research exchange.

    \item \textbf{SAKURA SCIENCE Exchange Program, Japan Science and Technology Agency (2023):}  
    Secured this prestigious fund as a Visiting Scholar to Japan in November 2023, supporting mobility and international collaboration in advanced research domains.
\end{itemize}

\subsection*{Research Funds}

\begin{itemize}
    \item \textbf{SmartDent (Global Seed Fund, 2024):}  
    Served as the co-Principal Investigator (co-PI) for this international pilot project focused on patient-specific machine learning-assisted additive manufacturing and real-time tracking of dental implants. The project emphasized both mobility and exploratory research, fostering interdisciplinary innovation.

    \item \textbf{AutoCAM\_SBO (Strategic Basic Research, 2024):}  
    Successfully secured funding for this 2.75-million-Euro project on AI-assisted CAD-to-CAM optimization for machining processes. My contributions included conducting preliminary exploratory research, engaging industrial partners to form a user group (mandatory for SBO projects), and drafting the proposal, which received approval in 2024.

    \item \textbf{National Natural Science Foundation of China (2018):}  
    The project focused investigations on a new approach of manufacturing surface functional microstructures using magnetic powder electrode discharge. 
    I contributed to drafting the proposal under the supervision of my supervisor. 
\end{itemize}

\clearpage
\end{document}