\documentclass[10pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
% \usepackage{hyperref}
% \hypersetup{
%     colorlinks=true,
%     linkcolor=blue,
%     filecolor=magenta,      
%     urlcolor=cyan,
%     pdftitle={Overleaf Example},
%     pdfpagemode=FullScreen,
%     }


\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Ming}{Wu}


\phone[mobile]{+32488390167}               
\email{ming.wu1@kuleuven.be}                             
\newcommand{\jobTitle}{\textbf{\textit{Tenure Track Assistant Professor position in Production Engineering"
}}}

\newcommand{\jobInstitution}{\textit{University of Oulu}}

\begin{document}
\recipient{To}{\jobInstitution
    }

\date{\today}
\opening{\textbf{Sub: Application for the \jobTitle}}
\closing{Your Sincerly, \vspace{-1em}}

\makelettertitle
Dear Hiring Committee,

I am pleased to apply for the Tenure Track Assistant Professor position in Production Engineering at the University of Oulu. With over 12 years of research experience in manufacturing processes, applied artificial intelligence (AI), and application-oriented additive manufacturing (AM), I have developed a robust interdisciplinary profile that aligns closely with the vision and objectives of your institution.

Throughout my academic journey, I have actively contributed to high-impact research initiatives, including two Horizon Europe 2020 projects and two National Natural Science Foundation of China (NSFC) projects, playing pivotal roles in drafting and securing successful proposals. Additionally, I have extensive experience with Flemish research programs spanning fundamental studies (e.g., SBO, KU Leuven C2) and applied projects (e.g., ICON, C3, IRVA). Notably, in 2023, I was the primary drafter of a 2.75 million Euro SBO project, achieving the highest evaluation score. These accomplishments underscore my ability to secure competitive funding, foster collaboration, and address critical challenges in production engineering.

Building on this foundation, in 2024, I co-initiated an interdisciplinary research project focusing on AM, AI, and in-process monitoring and control for clinical product development. My current work demonstrates a commitment to integrating advanced manufacturing technologies with AI to enable smarter, more sustainable production systems. These efforts align strongly with global trends and the mission of the Faculty of Technology to promote innovative and practical solutions in engineering.

Beyond research, I have developed a strong commitment to education and mentorship. As a daily supervisor for Ph.D. and master’s students, I have guided young researchers in advancing knowledge across manufacturing and AI domains. Additionally, my guest lectures on AI in Manufacturing have helped bridge the gap between theoretical understanding and practical application for engineering students. I am eager to continue fostering the next generation of engineers and innovators by contributing to curriculum development and interdisciplinary teaching initiatives at the University of Oulu.

If appointed, I aim to establish a research program at the interface of intelligent manufacturing and sustainable production systems, building on my expertise in AM, AI, and digital process monitoring. I am also enthusiastic about contributing to the university’s strategic priorities by collaborating across disciplines and engaging with industry partners to enhance innovation and societal impact.

I would be honored to bring my experience, skills, and vision to the Faculty of Technology at the University of Oulu. Thank you for considering my application. I welcome the opportunity to discuss my candidacy further and contribute to the continued excellence of your institution.

\vspace{0.5cm}

\makeletterclosing

\end{document}
